Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 algorithm_intro.tex
edits to algo intro, and problem statement

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
\item 
The conditional probability of pulling arm $i$ is less than
$1/\log(s)$ given current estimates \ArmEV{t}{i'} of arms'
attribute vectors.  In other words, we require
$\PullProb{t}{i} < 1/\log(s)$ where 
$\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
\cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i \pfedit{\mid \ArmEV{t}{i'}\ \forall i'}}$
is the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
\end{itemize}

@@

\pfcomment{I deleted here we now define $q(z)$ in section 2}
\pfdelete{
To capture the probability masses of problematic agents,
we define the quantity
$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
to be the total probability mass (across all arms) of agents
whose (actual) preference for their best arm over their second-best
arm is at most $\delta$.
}
\dkcomment{We should stress somewhere that we assume that actual ties
  have measure 0.}

>>>>

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
\item 
The conditional probability of pulling arm $i$ is less than
$1/\log(s)$ given current estimates \ArmEV{t}{i'} of arms'
attribute vectors.  In other words, we require
$\PullProb{t}{i} < 1/\log(s)$ where 
$\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
\cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i \mid \ArmEV{t}{i'}\ \forall i'}$
is the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
\end{itemize}

@@
